\bf Landslide: Systematic Testing in 15-410 \\ User Guide and Survey

### 2014-10-07 irb/survey.tex
fix typoo

\begin{enumerate}
	\item Clone the repository -- {\tt git clone https://github.com/bblum/landslide.git} -- this will be your workspace.
	\item Run {\tt ./p2-setup.sh PATH}, where {\tt PATH} is the absolute path to your p2 implementation.
		\begin{itemize}
			\item This command will import your p2 into {\tt ./pebsim/p2-basecode/} and then attempt to build it.
			\item {\tt PATH} should be the path with {\tt 410kern}, {\tt 410user}, {user/libthread}, etc as subdirectories, not the {\tt user/libthread} directory itself.
		\end{itemize}
	\item Next, make sure you have read this document entirely. At this point you should have several survey sheets printed out, ready to write on -- see the Survey section below. You should also have some means of timing yourself.
	\item Run {\tt ./landslide OPTIONS} to run tests with Landslide. {\bf Fill out a fresh survey sheet each time you do this.} Repeat until satisfied.
		\begin{itemize}
			\item Use {\tt ./landslide -h} to view command line options. The most important ones are {\tt -t}, max testing time, and {\tt -p}, which test program to run.
				% TODO: Remove this TODO when you have implemented glue to move the html files to the toplevel directory.
			\item Landslide's bug reports will show up as HTML files. If you are using a cluster machine in person, you can view them by pointing a browser to {\tt file:///PATH/TO/landslide/FILENAME.html}.
				\footnote{Another option: move it to {\tt \textasciitilde/www} in your AFS, and view it at {\tt http://www.contrib.andrew.cmu.edu/\textasciitilde{}YOUR\_ANDREWID/FILENAME.html}. Note the {\tt www} in the URL is mandatory; note also that this will allow the world to see it, so be careful!}
			\item The available test programs are {\tt thr\_exit\_join} (the default), {\tt broadcast\_test}, {\tt paraguay}, and {\tt rwlock\_downgrade\_read\_test}.
				\footnote{If you have your own custom test case, you can put it in {\tt pebsim/p2-basecode/user/progs} and edit \\ {\tt pebsim/p2-basecode/config.mk} to build it, then run {\tt ./p2-setup.sh} again.}
		\end{itemize}
\end{enumerate}

>>>>

\begin{enumerate}
	\item Clone the repository -- {\tt git clone https://github.com/bblum/landslide.git} -- this will be your workspace.
	\item Run {\tt ./p2-setup.sh PATH}, where {\tt PATH} is the absolute path to your p2 implementation.
		\begin{itemize}
			\item This command will import your p2 into {\tt ./pebsim/p2-basecode/} and then attempt to build it.
			\item {\tt PATH} should be the path with {\tt 410kern}, {\tt 410user}, {\tt user/libthread}, etc as subdirectories, not the {\tt user/libthread} directory itself.
		\end{itemize}
	\item Next, make sure you have read this document entirely. At this point you should have several survey sheets printed out, ready to write on -- see the Survey section below. You should also have some means of timing yourself.
	\item Run {\tt ./landslide OPTIONS} to run tests with Landslide. {\bf Fill out a fresh survey sheet each time you do this.} Repeat until satisfied.
		\begin{itemize}
			\item Use {\tt ./landslide -h} to view command line options. The most important ones are {\tt -t}, max testing time, and {\tt -p}, which test program to run.
				% TODO: Remove this TODO when you have implemented glue to move the html files to the toplevel directory.
			\item Landslide's bug reports will show up as HTML files. If you are using a cluster machine in person, you can view them by pointing a browser to {\tt file:///PATH/TO/landslide/FILENAME.html}.
				\footnote{Another option: move it to {\tt \textasciitilde/www} in your AFS, and view it at {\tt http://www.contrib.andrew.cmu.edu/\textasciitilde{}YOUR\_ANDREWID/FILENAME.html}. Note the {\tt www} in the URL is mandatory; note also that this will allow the world to see it, so be careful!}
			\item The available test programs are {\tt thr\_exit\_join} (the default), {\tt broadcast\_test}, {\tt paraguay}, and {\tt rwlock\_downgrade\_read\_test}.
				\footnote{If you have your own custom test case, you can put it in {\tt pebsim/p2-basecode/user/progs} and edit \\ {\tt pebsim/p2-basecode/config.mk} to build it, then run {\tt ./p2-setup.sh} again.}
		\end{itemize}
\end{enumerate}
